---
title: "MSC Datamart Download Script"
output: html_notebook
---

## Donovan Bangs
#### Last Updated: 7 July 2022



The Meteorological Service of Canada (MSC) offers climate and weather data available for download through its [MSC Datamart](https://dd.weather.gc.ca/). This script offers a quick means to read CSVs of daily meteorological data into your R session.

First, we need to define parts of the URL string. A complete path to a CSV will look like:

https://dd.weather.gc.ca/climate/observations/daily/csv/ON/climate_daily_ON_6104142_2008-12_P1D.csv

For December 2008 at the Kingston Climate Station (ID 6104142). 

Because we need to paste the year-month into the middle, we first define the fixed parts of the string:

```{r setup, warning=FALSE}
datamart_url <- "https://dd.weather.gc.ca/climate/observations/daily/csv/ON/"
sheet_name <- "climate_daily_ON_6104142_"
suffix <- "_P1D.csv"
```

Then let's define some years, and a list of months as characters.

```{r}
years <- 2008:2022
months <- c('01', '02', '03', '04', '05', '06', '07', '08', '09', '10', '11', '12')
```

With these pieces in place, we then initialize an empty data frame and loop through the years, inner loop the months, and ```rbind()``` each CSV. A ```tryCatch({})``` structure is included to skip "404 Not Found" errors for months and years that may not be in our range.

```{r eval=FALSE}
weather_data <- data.frame()

for(y in 1:length(years)){
  tryCatch({
    year = years[y]
  }, error=function(e){})

  for(m in 1:length(months)){
    tryCatch({
      month = months[m]
      
      string = paste(
        datamart_url,
        sheet_name,
        year,
        "-",
        month,
        suffix,
        sep = "")
      
      data_download <- read.csv(string)
      
      weather_data <- rbind(weather_data, data_download)
      
    }, error=function(e){})
  }
}
```
Now your session should include a ```weather_data``` frame with all of the available observations for the station identifier and years you've set above.
